\subsection{Experimental BMP}
The cumulative biogas production, daily biogas production, and methane content in the biogas produced during the digestion of SW from different production stages under mesophilic conditions are presented in Fig.1, Fig.2, and Fig.3.\\

Biogas production started immediately on the first 5 days of digestion in all reactors but those containing weaners wastewaters. Biogas production was very low in these digesters until day 9 when the gas production began to sustainably increase until day 14. Thereafter, biogas production remained relatively constant until day 21 before slowly decreasing and ceasing production in day 54. In the reactors containing gestation and fattening wastewaters, biogas production rapidly increased until days 14 and 9, respectively, before continuously decrease until the end of the experiment. Peak values for the daily biogas production rate were calculated to be 26.1, 14.6, and 18.6 ml.gVS added\textsuperscript{-1} after 14, 14, and 9 days for swine wastewater from gestation, weaners, and fattening stages, respectively.
Farrowing wastewater showed no detectable biogas production in the studied conditions due to their very low organics content as measured by VS and COD; in reality, however, some biogas was likely produced during the experiment but in such a low amount that it was not measureable gravimetrically.\\
Gestation wastewater presented the largest average biogas potential after 61 days (491.01 (40.07) ml.gVS added\textsuperscript{-1}) followed by fattening (391.71 (356.07) ml.gVS added\textsuperscript{-1}) and weaners (240.95 (2.07) ml.g VS added\textsuperscript{-1}) wastewater. ANOVA on the cumulative biogas production showed no statistically significant differences between different stages. As shown in Fig. 1, most of the final biogas yields were obtained in the first 28-36 days of digestion for each production stage, specifically 89.8\%, 92.7\%, and 84.4\% for fattening, gestation and weaners wastewater, after 28, 36, and 36 days,

The methane content in the biogas produced